---
title: "Linear Regression Assignment 1"
author: "145054_Henry_Kyalo"
date: "2/25/2022"
output:
  word_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
```{r}
#importing packages
library(readxl)
library(dplyr)
library(ggplot2)
library(ggpubr)
```
In this data, i intend to to do a simple linear regresion and linear mod of predicting salaries depending on the years of experience that one has in the market.

 

```{r}
df<-read_excel("Data1.xlsx")
```
```{r}
# inspecting the data
head(df)
```

```{r}
# any missing values?
sum(is.na(df))
```
The dataset has no missing values as the sum of is.na () function returns 0.
```{r}
#getting summary statistics of the dataset
summary(df)
```
```{r}
# checking for normality of the dependent variables using hist function
hist(df$`Years of Experience`)
```

```{r}
#checking for linearity of independent and dependent variable
plot(Salaries ~ `Years of Experience`,data=df)
```
From the plot above, we can conclude that there is some linearity around our data points, although most of the points are likely to be outliers.
```{r}
# performing linear regression model
salaries.yearsofexperience.lm<-lm(Salaries ~ `Years of Experience`,data = df)
summary(salaries.yearsofexperience.lm)
```
From the table above, we can conclude that there is significant positive relationship between Salaries and years of experience (P-value < 0.001), with a 93.645 unit increase in Salaries for every unit increase in  years of experince. 
```{r}
#Checking for simple regression homoscedasticity
par(mfrow=c(2,2))
plot(salaries.yearsofexperience.lm)
par(mfrow=c(1,1))
```
Looking at the red lines, they are not horizontal or centered around zero, and therefore, this means our data has outliers or biases which could render our linear regression invalid.
```{r}
#visualizing the results with a graph
salaries.graph<-ggplot(df,aes(x=`Years of Experience`,y=Salaries))+
  geom_point()
salaries.graph
```
```{r}
#adding linear regression to the plotted graph
salaries.graph<-salaries.graph + geom_smooth(model='lm',col='black')
salaries.graph
```



